### 2024-08-02 download-football-data.qmd
20240802 - fix duplicate identifier
20240802 - update indentation

## Load Packages {#sec-loadPackages}

@@

nfl_4thdown_raw <- nfl4th::load_4th_pbp(seasons = 2014:nflreadr::most_recent_season())
```

@@

nfl_advancedStatsPFR_weekly <- nfl_advancedStatsPFR_weekly %>% 
  mutate(
    player_name = coalesce(
      player_name.pass,
      player_name.rush,
      player_name.rec,
      player_name.def
    ),
    ,
    season = coalesce(
      season.pass,
      season.rush,
      season.rec,
      season.def
    ),
    week = coalesce(
      week.pass,
      week.rush,
      week.rec,
      week.def
    ),
    team = coalesce(
      team.pass,
      team.rush,
      team.rec,
      team.def
    )
  ) %>% 
  select(-c(starts_with("player_name.")))

>>>>

## Load Packages {#sec-downloadFootballDataLoadPackages}

@@

nfl_4thdown_raw <- nfl4th::load_4th_pbp(
  seasons = 2014:nflreadr::most_recent_season())
```

@@

nfl_advancedStatsPFR_weekly <- nfl_advancedStatsPFR_weekly %>% 
  mutate(
    player_name = coalesce(
      player_name.pass,
      player_name.rush,
      player_name.rec,
      player_name.def
    ),
    season = coalesce(
      season.pass,
      season.rush,
      season.rec,
      season.def
    ),
    week = coalesce(
      week.pass,
      week.rush,
      week.rec,
      week.def
    ),
    team = coalesce(
      team.pass,
      team.rush,
      team.rec,
      team.def
    )
  ) %>% 
  select(-c(starts_with("player_name.")))
